%-------------------------PACKAGES-------------------------%


\documentclass[9pt]{extarticle}
% \usepackage[margin=0.2in]{geometry}
\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=5mm,
 top=5mm,
 bottom=3mm,
 right=5mm,
 }
\usepackage{romannum}
\usepackage{hyperref}
\usepackage[most]{tcolorbox}
\usepackage{fontawesome}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}
\let\orighref\href

% \definecolor{debianred}{rgb}{0.84, 0.04, 0.33}

% \usepackage[sfdefault]{carlito}
\usepackage{multicol}
\setlist[itemize]{noitemsep, topsep=0pt}
\addtolength{\parskip}{-1.5mm}
\tcbset{
    frame code={}
    center title,
    left=0pt,
    right=0pt,
    top=0pt,
    bottom=0pt,
    colback=gray!50,
    colframe=white,
    width=\dimexpr\textwidth\relax,
    enlarge left by=0mm,
    boxsep=3pt,
    arc=0pt,outer arc=0pt,
    }
% \usepackage{fontspec}
% \setmainfont{}


%-------------------------PACKAGES-------------------------%


\begin{document}
\begin{center}


%-------------------------HEADER-------------------------%


\noindent {\Huge\textbf{Aman Khilani}}
\vspace{2pt}\\

$3^{rd}$ Year Undergraduate \(|\) Department of Civil Engineering at IIT Kanpur\\
\vspace{0pt}

\faEnvelope~\href{mailto:amanrk21@iitk.ac.in}{amanrk21@iitk.ac.in}
\faGithub~\href{https://github.com/doomsday4}{aman-khilani-github}
\faPhone~\href{tel:+918239934455}{+91 8239934455}
\faLinkedin~\href{https://www.linkedin.com/in/aman-khilani/}{aman-khilani-linkedin}



%-------------------------HEADER-------------------------%

\begin{center}
\end{center}

\vspace{-18pt} % space b/w the line and contact details

\noindent\rule[0.5ex]{\linewidth}{1pt}

\vspace{-18pt} % space b/w line and academic qualifications


%-------------------------ACADEMIC QUAL-------------------------%


{\large \textbf{\begin{tcolorbox}\textsc{Academic Qualifications}\end{tcolorbox}}}
\vspace{-10pt}
\begin{center}
\begin{tabular}{|p{2.5cm}|p{5.0cm}|p{8.6cm}|p{1.8cm}|}
\hline
    \centering{\textbf{Year}} & \centering{\textbf{Degree/Certificate}} & \centering{\textbf{Institute}} & \textbf{CPI/$\%$}\\
\hline
    \centering{2021} - Present & \centering{B.Tech} & \centering{Indian Institute of Technology Kanpur} & 8.6/10\\
\hline
    \centering{2021} & \centering{CBSE(\Romannum{12})} & \centering{Vrindavan Public School, Ajmer} & 93.20$\%$\\
\hline
    \centering{2019} & \centering{CBSE(\Romannum{10})} & \centering{St. Anselm's Sr. Sec. School, Ajmer} & 92.80$\%$\\
\hline
\end{tabular}
\end{center}


%-------------------------ACADEMIC QUAL-------------------------%

\vspace{-10pt}

%-------------------------SCHOLASTIC ACHIEVEMENTS-------------------------%


{\large \textbf{\begin{tcolorbox}\textsc{Scholastic Achievements}\end{tcolorbox}}}
\vspace{-10pt}

\begin{itemize}
    \item Granted the prestigious \textbf{K.N. Saluja Scholarship} for the 2022-23 tenure, given to the \textbf{Top 2} students of the CE batch.
    \item Ranked among the \textbf{Top 3.3\%} in the \textbf{Joint Entrance Examination (Advanced) 2021} among the \textbf{1.5 Lakhs} shortlisted candidates.
    \item Secured one of the \textbf{Top 1.3\%} positions in the \textbf{Joint Entrance Examination (Main) 2021} among \textbf{9 Lakh} candidates.
    \item Participated in competitive exams like \textbf{NTSE, STSE, IMO and KVPY}.
\end{itemize}
\medskip


%-------------------------SCHOLASTIC ACHIEVEMENTS-------------------------%

\vspace{-20pt}

%-------------------------WORK EXPERIENCE-------------------------%


{\large \textbf{\begin{tcolorbox}\textsc{Work Experience}\end{tcolorbox}}}
\vspace{-10pt}

% Vibinex Intern
\vspace{0pt}
\begin{itemize}
    \item \textbf{\href{https://github.com/doomsday4/chrome-extension-Vibinex.git}{Vibinex Intern}} $\vert$ SUMMER INTERNSHIP $\vert$\hfill\hfill(\textit{Jun'23- Present})\\{Mentor: Mr. Avikalp Kumar Gupta}
\begin{itemize}[leftmargin = 0.2cm]
    \item Refactored and modularized the codebase of the company's main service, a Chrome extension designed to track pull requests and commits on GitHub and Bitbucket repositories.
    \item Contributed to the development and enhancement of the company website by integrating and setting up \textbf{\href{https://github.com/doomsday4/team-monitor-website/blob/main/pages/_app.tsx}{Microsoft Clarity}}. This enabled us to gain valuable insights into user interactions, helping us optimize and improve the overall user experience on the website.
\end{itemize}
\end{itemize}
\medskip

%-------------------------WORK EXPERIENCE-------------------------%

\vspace{-20pt}

%-------------------------KEY PROJECTS-------------------------%


{\large \textbf{\begin{tcolorbox}\textsc{Key Projects}\end{tcolorbox}}}

\vspace{-10pt}

%-- Robofest --%
\vspace{0pt}
\begin{itemize}
    \item \textbf{\href{https://drive.google.com/file/d/1IwhenBLTY_WEnSnDKVB_pcYu46HWAsuG/view?usp=sharing}{ROBOFEST GUJRAT 3.0 }} $\vert$ TECH COMPETITION $\vert$\hfill\hfill(\textit{Dec'22- Jan'23})\\{Team AUV, IITK}
\begin{itemize}[leftmargin = 0.2cm]
    \item Stood \textbf{1st} in the Level 1 of the ROV competition in the Under Water category, organised by \textbf{GUJCOST}, along with 4 other members, representing Team AUV from IITK.
    \item Created the ideataion for a \textbf{Remotely Operated Underwater Vehicle}, explaining all it's structural, electronic and software components with a detailed methodology on how the actual robot will work.
    \item Contributed in the software methodology.
\end{itemize}
\end{itemize}

%-- Rover Base --%
\vspace{0pt}
\begin{itemize}
    \item \textbf{{ROVER BASE }} $\vert$ SUMMER PROJECT $\vert$\hfill\hfill(\textit{May'22- Jul'22})\\{Robotics Club, IITK}
\begin{itemize}[leftmargin = 0.2cm]
    \item Learned about \textbf{Fusion 360} and used it to generate a 3D model of the different parts of the rover base.
    \item Implemented \textbf{Matlab} to set the geometric dimensions of the model in accordance with its physics.
    \item Created \textbf{ROS Nodes} in Matlab. Tested the Robotics algorithms on \textbf{Gazebo} simulator.
\end{itemize}
\end{itemize}

%-- Mathematical Tools for Data Science --%
\vspace{0pt}
\begin{itemize}
    \item \textbf{\href{https://github.com/doomsday4/Mathematical-Tools-for-Data-Science-1.git}{MATHEMATICAL TOOLS FOR DATA SCIENCE }} $\vert$ STAMATICS PROJECT $\vert$ \hfill\hfill(\textit{Apr'22- Jun'22})\\{Stamatics Society, IIT Kanpur}
\begin{itemize}[leftmargin = 0.2cm]
    \item Learned and implemented concepts related to \textbf{Data Science} and used \textbf{Python} to analyse and visualise different kinds of datasets.
    \item Practical application of the concepts of \textbf{Linear Algebra, Probability and Statistics}.
    \item Python libraries used- Numpy, Pandas, Matplotlib and Seaborn.
\end{itemize}
\end{itemize}
\medskip


%-------------------------KEY PROJECTS-------------------------%

\vspace{-20pt}

%-------------------------SELF PROJECTS-------------------------%
{\large \textbf{\begin{tcolorbox}\textsc{Self Projects}\end{tcolorbox}}}
\vspace{-10pt}

%-- VS Code Extension --%
\begin{itemize}
    \item \textbf{\href{https://github.com/doomsday4/VSCodeExtension-LastEditor.git}{VS Code Extension }} : \textbf{Developed} a custom VS Code extension that integrates with Git to provide real-time information about code contributors based on the \textbf{Git blame data}. The extension intelligently identifies and displays the username of the last person who made changes to a specific line of code within the repository.
    \item \textbf{\href{https://linktree-clone-doomsday4.vercel.app/}{Linktree Clone}} : {Created a personalized link management tool inspired by the popular Linktree platform, using a combination of \textbf{HTML, CSS, and JavaScript}.It offers a user-friendly interface to organize and share multiple links through a single customizable page. The Linktree clone has been \textbf{deployed and hosted using the Vercel service}}
    \item\textbf{\href{https://github.com/doomsday4/sentiment_analysis}{Sentiment Analysis Model }} : Developed a robust sentiment analysis model using \textbf{Logistic Regression} to extract data and accurately \textbf{predict customer responses} based on their reviews. This model enables effective analysis of customer sentiments towards products or services, aiding in \textbf{decision-making} and enhancing overall customer satisfaction.
\end{itemize}
\medskip

%-------------------------SELF PROJECTS-------------------------%

\vspace{-20pt}

%-------------------------TECHNICAL SKILLS-------------------------%
{\large \textbf{\begin{tcolorbox}\textsc{Technical Skills}\end{tcolorbox}}}
\vspace{-10pt}

\begin{itemize}
    \item \textbf{Programming Languages/Frameworks: }C/C++, Python, HTML, CSS, JavaScript, Matlab
    \item \textbf{Software: }Xcode, VS Code, Sublime, Adobe Lightroom, Photoshop, After Effects, Premiere Pro, DaVinci Resolve
    \item \textbf{Utilities: }Git, Bash, Linux, \LaTeX, Numpy, Pandas, Matplotlib, Seaborn, ROS, SLAM, Gazebo, Rviz
\end{itemize}
\medskip

%-------------------------TECHNICAL SKILLS-------------------------%

\vspace{-20pt}

%-------------------------RELEVANT COURSES-------------------------%
{\large \textbf{\begin{tcolorbox}\textsc{Relevant Courses}\end{tcolorbox}}}
\vspace{-10pt}

\begin{center}
    \begin{tabular}{|p{7cm}|p{10cm}|p{5.5cm}|}
    \hline
    \textbf{(HSO201)} Applied Probability and Statistics & \textbf{(ESC210)} Introduction to Electronics\\
    \textbf{(ESC101)} Fundamentals of Computing &  \textbf{(MTH 102)} Linear Algebra and Ordinary Differential Equations\\
    \textbf{(Udemy)} Data Science using Python & \textbf{(MSO203B)} Partial Differential Equations\\
    \hline
    \end{tabular}\\
\vspace{2pt}
\end{center}
\hspace{15pt}

%-------------------------RELEVANT COURSES-------------------------%

\vspace{-20pt}

%-------------------------POSITION OF RESPONSIBILITY-------------------------%
{\large \textbf{\begin{tcolorbox}\textsc{Position of Responsibility}\end{tcolorbox}}}
\vspace{-10pt}

\begin{itemize}
    \item \textbf{STUDENT GUIDE} | COUNSELLING SERVICE, IITK\hfill\hfill(\textit{Nov'22- Present})
    \begin{itemize}[leftmargin = 0.2cm]
    \item \textbf{Guided and mentored} a group of five freshmen students throughout their first year, providing invaluable support and advice.
    \item Collaborated effectively with a team of fellow Student Guides and CTMs to organise a comprehensive \textbf{9 day orientation program} for \textbf{1200+ freshmen students}, ensuring a smooth transition into college life.
    \item Fostered a welcoming and inclusive environment, creating opportunities for freshmen students to connect, engage, and form lasting relationships.
    \end{itemize}
    \medskip
    \item \textbf{COORDINATOR} | FILM CLUB, IITK\hfill\hfill(\textit{May'23- Present})
    \begin{itemize}[leftmargin = 0.2cm]
    \item \textbf{Organised} cinematography and editing workshops for freshmen students, providing them with practical skills and knowledge in the field of filmmaking.
    \item Successfully participated in the prestigious \textbf{IFP 51hrs Filmmaking Challenge} during my tenure as the Film Club Secretary, where our team's submission received a nomination for the \textbf{first time in the club's history}. Out of \textbf{1600 entries}, our film was recognized as one of the \textbf{top 48}, highlighting our team's creativity and storytelling abilities.
    % \item Demonstrated effective leadership and teamwork as the Coordinator of the Film Club, fostering a collaborative environment among members, and facilitating opportunities for students to explore their passion for filmmaking while developing their technical skills and artistic vision.
    \end{itemize}
\end{itemize}

%-------------------------POSITION OF RESPONSIBILITY-------------------------%

\end{center}
\end{document}

